Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-02-29 ms.tex
various minor edits

The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images represent
the input data for our W1/W2 coadds. Specifically, for each L1b frameset, we 
make use of the per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, 
which respectively give the measured sky intensity and associated per-pixel 
bitmask values and uncertainty estimates. We have obtained a local copy of 
these files for every W1 and W2 frameset, including those from the AllWISE 
release ($\sim$2.8M framesets) and first-year NEOWISER release ($\sim$2.5M 
framesets). In all we have analyzed $\sim$5.3M framesets in each of W1 and 
W2, corresponding to a total of $\sim$32M L1b image files, $\sim$71TB of 
input image data and $\sim$33$\times$10$^{12}$ pixels.

@@

% mention that we use the same tile centers as Atlas and original unWISE
Like the official WISE Atlas coadds, unWISE processing divides the sky
into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
arranged along iso-declination rings. Unlike the Atlas stacks, the
unWISE code uses Lanczos interpolation to preserve the native WISE 
angular resolution during coaddition, creating stacked outputs which are 2048 
pixels on a side, with 2.75$''$ pixels.

@@

We desired a photometic calibration with time resolution of one day. To
achieve this, we grouped our single-exposure photometric measurements in two 
ways. First, for each 
unique source, we lumped all of its All-Sky phase measurements together to 
obtain its median flux (DN) in our aperture photometry system during this 
phase. This is justified because the All-Sky release photometric zero points 
are known to be remarkably stable \citep{jarrett11}. Indeed, using our ecliptic
pole singe-exposure photometry database, we were able to confirm that the 
All-Sky phase zero point was stable at the $\le$2 mmag level in both bands. 
Next, for every aperture flux after the All-Sky phase, we calculated a 
multiplicative enhancement factor
implied by the ratio of that measurement to the appropriate source's
median All-Sky phase flux. We then grouped these 
multiplicative enhancement factors into one-day bins, and quote the median per 
bin as the change in multiplicative
image scaling relative to the All-Sky zero point. For the  
All-Sky phase zero points, we adopted the \verb|MAGZP| values of 20.752 in W1 
and 19.596 in W2.

@@

Figure \ref{fig:warp_example} provides an illustration of our polynomial 
background modeling procedure. We were able to recover 54\% of 
Moon-contaminated data in W1 and 33\% in W2. We also apply this polynomial
correction procedure to frames that we flagged as potentially affected
by scattered light halos from bright solar system planets.

@@

Figure \ref{fig:image_noise} shows zoom-ins of low ecliptic latitude fields 
which illustrate visually the reduction in statistical noise which has been 
achieved by doubling the number of input exposures.

@@

\begin{figure*}[ht]
 \begin{center}
  \epsfig{file=w1_image_noise.eps, width=6.0in}
  \caption{\label{fig:image_noise} Example of reduced image noise
           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
           This is a representative location at low ecliptic latitude and high 
           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
           images are rendered with identical color stretches.}
 \end{center}
\end{figure*}

@@

\acknowledgments{
We thank Roc Cutri for his guidance in making use of the WISE data products. 
We thank Stephen Bailey for downloading the L1b images to NERSC. We thank
Doug Finkbeiner for providing access to the big-memory computers which
were used to run coadds near the ecliptic poles. We thank Peter Nugent for 
providing HPC assistance. We thank many members of the DECaLS/MzLS data team for
valuable feedback, especially Arjun Dey, Doug Finkbeiner, John Moustakas
and Bob Blum.

>>>>

The 1016 pixel by 1016 pixel WISE single-exposure ``L1b'' images represent
the input data for our W1/W2 coadds. Specifically, for each L1b frameset, we 
make use of the per-band \verb|-int-|, \verb|-msk-| and \verb|-unc-| images, 
which respectively give the measured sky intensity and associated per-pixel 
bitmask values and uncertainty estimates. We have obtained a local copy of 
these files for every publicly available W1 and W2 frameset, including those 
from the AllWISE release ($\sim$2.8M framesets) and first-year NEOWISER release
($\sim$2.5M framesets). In all we have analyzed $\sim$5.3M framesets in each of
W1 and W2, corresponding to a total of $\sim$32M L1b image files, $\sim$71TB of 
input image data and $\sim$33$\times$10$^{12}$ pixels.

@@

% mention that we use the same tile centers as Atlas and original unWISE
Like the official WISE Atlas coadds, unWISE processing divides the sky
into a set of 18240 $\sim$1.5$^{\circ}$$\times$$\sim$1.5$^{\circ}$ tiles
arranged along iso-declination rings. Whereas the Atlas images
are smoothed by the WISE PSF, the unWISE code uses Lanczos interpolation to 
preserve the native WISE angular resolution during coaddition, creating stacked
outputs which are 2048 pixels on a side, with 2.75$''$ pixels.

@@

We desired a photometic calibration with time resolution of one day. To
achieve this, we grouped our single-exposure aperture photometry measurements 
in two ways. First, for each 
unique source, we lumped all of its All-Sky phase measurements together to 
obtain its median flux (DN) in our aperture photometry system during this 
phase. This is justified because the All-Sky release photometric zero points 
are known to be remarkably stable \citep{jarrett11}. Indeed, using our ecliptic
pole singe-exposure photometry database, we were able to confirm that the 
All-Sky phase zero point was stable at the $\le$2 mmag level in both bands. 
Next, for every aperture flux after the All-Sky phase, we calculated a 
multiplicative enhancement factor
implied by the ratio of that measurement to the appropriate source's
median All-Sky phase flux. We then grouped these 
multiplicative enhancement factors into one-day bins, and quote the median per 
bin as the change in multiplicative
image scaling relative to the All-Sky zero point. For the  
All-Sky phase zero points, we adopted the \verb|MAGZP| values of 20.752 in W1 
and 19.596 in W2.

@@

Figure \ref{fig:warp_example} provides an illustration of our polynomial 
background modeling procedure applied to a single L1b quadrant. We were able to 
recover 54\% of Moon-contaminated data in W1 and 33\% in W2. We also apply this
polynomial correction procedure to frames that we flagged as potentially 
affected by scattered light halos from bright solar system planets.

@@

Figure \ref{fig:image_noise} shows zoom-ins of a low ecliptic latitude field,
illustrating visually the reduction in statistical noise which has been 
achieved by doubling the number of input exposures.

@@

\begin{figure*}[ht]
 \begin{center}
  \epsfig{file=w1_image_noise.eps, width=6.0in}
  \caption{\label{fig:image_noise} Example of reduced image noise
           in W1 for a $\sim$6$'$ cutout extracted from tile 3353m107, centered
           at ($\alpha$, $\delta$) = (335.4585$^{\circ}$, $-$10.5801$^{\circ}$). 
           This is a representative location at low ecliptic latitude and high 
           Galactic latitude,  with $\sim$2$\times$ as much coverage in our 
           AllWISE+NEOWISER coadd relative to that of \cite{lang14}. Both
           images are rendered with identical grayscale stretches.}
 \end{center}
\end{figure*}

@@

\acknowledgments{
We thank Roc Cutri for his guidance in making use of the WISE data products. 
We thank Stephen Bailey for downloading the L1b images to NERSC. We thank
Doug Finkbeiner for providing access to the big-memory computers which
were used to run coadds near the ecliptic poles. We thank Peter Nugent for 
data management and HPC assistance. We thank many members of the DECaLS/MzLS 
data team for valuable feedback, especially Arjun Dey, Doug Finkbeiner, John 
Moustakas and Bob Blum.
